---
title: "Import the data"
output: html_notebook
---

Import data from the original PLS files. See README in the `data` directory for
the expected file layout.

```{r}
library(tidyverse)
library(arrow)
library(data.table)
library(dtplyr)
source("../lib/parsers.R")
```
```{r}
panel_sched <- tribble(
  ~year,~quarter,~visit,~panel,
  1,"Q1","V1","P11",
  1,"Q2","V2","P11",
  1,"Q3","V3","P11",
  1,"Q4","V4","P11",
  
  1,"Q2","V1","P12",
  1,"Q3","V2","P12",
  1,"Q4","V3","P12",
  2,"Q5","V4","P12",
  
  1,"Q3","V1","P13",
  1,"Q4","V2","P13",
  2,"Q5","V3","P13",
  2,"Q6","V4","P13",
  
  1,"Q4","V1","P14",
  2,"Q5","V2","P14",
  2,"Q6","V3","P14",
  2,"Q7","V4","P14",
  
  2,"Q5","V1","P15",
  2,"Q6","V2","P15",
  2,"Q7","V3","P15",
  2,"Q8","V4","P15",
  
  2,"Q6","V1","P16",
  2,"Q7","V2","P16",
  2,"Q8","V3","P16",
  3,"Q1","V4","P16",
  
  2,"Q7","V1","P17",
  2,"Q8","V2","P17",
  3,"Q1","V3","P17",
  3,"Q2","V4","P17",
  
  2,"Q8","V1","P18",
  3,"Q1","V2","P18",
  3,"Q2","V3","P18",
  3,"Q3","V4","P18",
  
  3,"Q1","V1","P21",
  3,"Q2","V2","P21",
  3,"Q3","V3","P21",
  3,"Q4","V4","P21",
  
  3,"Q2","V1","P22",
  3,"Q3","V2","P22",
  3,"Q4","V3","P22",
  
  3,"Q3","V1","P23",
  3,"Q4","V2","P23",
  
  3,"Q4","V1","P24"
)
```

Read in all the household-level files.

```{r}
hhfv17 <- parse_hh("../../data/2017-18/FHH_FV.TXT.xz",1) |> setDT()
hhrv17 <- parse_hh("../../data/2017-18/FHH_RV.TXT.xz",1) |> setDT()
```


```{r}
hhfv18 <- parse_hh("../../data/2018-19/hh104_fv_final.txt.xz",2) |> setDT()
hhrv18 <- parse_hh("../../data/2018-19/hh104_rv_final.txt.xz",2) |> setDT()
```


```{r}
hhfv19 <- parse_hh("../../data/2019-20/HHV1.TXT.xz",3) |> setDT()
hhrv19 <- parse_hh("../../data/2019-20/HHRV.TXT.xz",3) |> setDT()
```

Combine them, select only the urban households, identify the panel
using the panel schedule and create the unique household identifier.

```{r}
all_urban_hh <- rbind(hhfv17,hhrv17,hhfv18,hhrv18,hhfv19,hhrv19,fill=TRUE) |>
  filter(sector==2) |>
  left_join(panel_sched,
            by=c("year","quarter","visit"))|>
  mutate(uhid=paste(panel,uhid,sep="|")) |>
  as.data.table() |>
  setkey(uhid)
rm(hhfv17,hhrv17,hhfv18,hhrv18,hhfv19,hhrv19)
```

Check if religion or social group changes.

```{r}
h.relg.grp.mismatch <-
  all_urban_hh |>
  group_by(uhid) |>
  distinct(religion,social_group)|>
  count() |>
  filter(n>1) |>
  ungroup() |>
  select(uhid) |>
  distinct() |>
  as.data.table()
```

Check if household size has unusual changes

```{r}
h.size.mismatch <-
  all_urban_hh |>
  group_by(uhid) |>
  summarize(m=min(hh_size),M=max(hh_size))|>
  filter(M-m>3) |>
  ungroup() |>
  select(uhid) |>
  distinct() |>
  as.data.table()
```

Tabulate the number of households

```{r}
all_urban_hh |>
  group_by(panel,year,quarter,visit) |>
  summarize(n=n()) |>
  as_tibble()
```

Read in all the person-level files.

```{r}
pfv17 <- parse_pfv("../../data/2017-18/FPER_FV.TXT.xz",1) |> setDT()
```

```{r}
# Quarters seem to be miscoded in this file
prv17 <- parse_prv("../../data/2017-18/FPER_RV.TXT.xz",1)|>
  mutate(quarter=case_when(
    quarter=="Q3"~"Q2",
    quarter=="Q4"~"Q3",
    quarter=="Q5"~"Q4"
  )) |>
  setDT()
  
```

```{r}
pfv18 <- parse_pfv("../../data/2018-19/per104_fv_final.txt.xz",2) |> setDT()
```

```{r}
prv18 <- parse_prv("../../data/2018-19/per104_rv_final.txt.xz",2) |> setDT()
```

```{r}
pfv19 <- parse_pfv("../../data/2019-20/PERV1.TXT.xz",3) |> setDT()
```

```{r}
prv19 <- parse_prv("../../data/2019-20/PERRV.TXT.xz",3) |> setDT()
```

Combine them, identify the panels, assign unique id.

```{r}
all_urban_pers <- rbind(pfv17,prv17,pfv18,prv18,pfv19,prv19,fill=TRUE) |>
  filter(sector==2) |>
  left_join(panel_sched,
            by=c("year","quarter","visit"))|>
  mutate(uhid=paste(panel,uhid,sep="|"),
         upid=paste(panel,upid,sep="|")) |>
  as.data.table() |>
  setkey(uhid,upid)
rm(pfv17,prv17,pfv18,prv18,pfv19,prv19)
```

See if sex or relation to head of household changes.

```{r}
p.sex.rel.mismatch <- 
  all_urban_pers |>
  group_by(uhid,upid) |>
  distinct(sex,rel_to_head) |>
  count() |>
  filter(n>1) |>
  ungroup() |>
  select(uhid) |>
  distinct() |>
  as.data.table()
```
See if there is an unusual change in age.

```{r}
p.age.mismatch <- 
  all_urban_pers |>
  group_by(uhid,upid) |>
  summarize(m=min(age),M=max(age)) |>
  filter(M-m>4)|>
  ungroup() |>
  select(uhid) |>
  distinct() |>
  as.data.table()
```
## Drop bad matches

Combined list of all households that fail validation tests.

```{r}
bad_matches <- 
  rbind(h.size.mismatch,h.relg.grp.mismatch,
            p.age.mismatch,p.sex.rel.mismatch) |>
  distinct() |>
  as.data.table()
```

Drop households and all persons in them that fail tests.

```{r}
all_urban_pers <- anti_join(all_urban_pers,bad_matches,by="uhid") |>
  as.data.table()
all_urban_hh <- anti_join(all_urban_hh,bad_matches,by="uhid") |>
  as.data.table()
```

Tabulate the number of persons remaining after validation.

```{r}
all_urban_pers |>
  group_by(panel,year,quarter,visit)|>
  summarize(n=n()) |>
  arrange(panel,year,quarter,visit) |>
  as_tibble()
```

Save.


```{r}
write_parquet(setDF(all_urban_hh),"../../artefacts/linked_hh.parquet",
              version=2,compression="gzip")
```

```{r}
write_parquet(setDF(all_urban_pers),"../../artefacts/linked_pers.parquet",
              version=2,compression="gzip")
```

